Title of the Master Thesis

### 2016-03-06 Master Thesis/synopsis.tex
Fix group index notation

\begin{proof}
The degree $[K(\mu_\ell, \sqrt{-1}):K]$ is prime to $\ell$, thus we can assume that $\mu_\ell\subset K$ and $K$ is not formally real without loss of generality. Now, we can replace $\mathbb{Z}/\ell\mathbb{Z}$ by $\mathbb{Z}/\ell\mathbb{Z}(2) = \mu_\ell^{\otimes 2}$.

@@

The second assertion follows from the first one, applied to $L$, by using the following equation of supernatural numbers ([E], Theorem 20.21):
\[ [L:K] = [\Gamma':\Gamma][k':k]\cdot p^d \]
for some $d \leq \infty$, where $\Gamma'$ denotes the value group and $k'$ the residue field of the unique prolongation of $w$ to $L$.
\end{proof}

>>>>

\begin{proof}
The degree $[K(\mu_\ell, \sqrt{-1}):K]$ is prime to $\ell$, thus we can assume that $\mu_\ell\subset K$ and $K$ is not formally real without loss of generality. Now we can replace $\mathbb{Z}/\ell\mathbb{Z}$ by $\mathbb{Z}/\ell\mathbb{Z}(2) = \mu_\ell^{\otimes 2}$.

@@

The second assertion follows from the first one, applied to $L$, by using the following equation of supernatural numbers ([E], Theorem 20.21):
\[ [L:K] = (\Gamma':\Gamma) \cdot [k':k]\cdot p^d \]
for some $d \leq \infty$, where $\Gamma'$ denotes the value group and $k'$ the residue field of the unique prolongation of $w$ to $L$.
\end{proof}
